\documentclass[cover.tex]{subfiles}


\begin{document} 


\begin{mdframed}[style=MyFrame]
\begin{center}{\textcolor{red}{\Large Lecture policies}}\end{center}
\begin{enumerate}
\item If you signed up to class late and start the semester later than regular students, you have 5 days from when you are officially listed to class to hand out any missing HW, lab work (pre and post lab), and take any quiz. After that period you will not receive any points for missing work.
\item Lab and HW components of the grade will only be taken into account if you quiz average is above 60.
\item If you miss the final quiz your final grade will be commputed using a zero for the final quiz.
\item There are no make-ups for missed quizzes or HW.
\item If you submit any HW late you will substracted 5 points a day.
\item You need to bring a scientific calculator to class and your phone does not count as one.
\item For level 2 classes (CHEM 202) you need a graphing calculator (Casio is a good brand)
\item Class work can only be done during class, hence your attendance is critical for this grade component.
\item If you miss a class with a classwork component you miss the corresponding grade.
\item You may bring a cheat sheet on 8.5x11 paper to the exam. No more than a single sheet will be allowed under any circumstance. If you are seen in a quiz with more than a single page, the instructor has the right to reduce your quiz grade by 20 points.
\item Assignments in which you had tech issues during submission will waived unless you reach out on the day of the deadline.
\end{enumerate}
 
    \par\noindent\makebox[1.5in]{\hrulefill}   \hfill\makebox[2.0in]{\hrulefill}    \hfill\makebox[2.0in]{\hrulefill}  \par\noindent\makebox[1.5in][l]{Name}    \hfill\makebox[2.0in][l]{Signature}   \hfill\makebox[2.0in][l]{Date} 
 

\end{mdframed}

\end{document}
