\documentclass[cover.tex]{subfiles}


\begin{document} \begin{refsection}

\begin{multicols*}{2}
\begin{enumerate}

\item Flammable materials, like alcohol, should never be dispensed or used near. Chose the most correct answer.
\begin{enumerate}[label=(\alph*)]
\item an open door.
\item an open flame.
\item another student.
\item a sink.
\end{enumerate}

\item If a laboratory fire erupts, immediately
\begin{enumerate}[label=(\alph*)]
\item notify your instructor.
\item run for the fire extinguisher.
\item throw water on the fire.
\item open the windows.
\end{enumerate}

\item Approved eye protection devices (such as goggles) are worn in the laboratory
\begin{enumerate}[label=(\alph*)]
\item to avoid eye strain.
\item to improve your vision.
\item only if you do not have corrective glasses.
\item any time chemicals, heat, or glassware are used.
\end{enumerate}

\item If you wear contact lenses in the school laboratory,
\begin{enumerate}[label=(\alph*)]
\item take them out before starting the lab.
\item you do not have to wear protective goggles.
\item advise your science instructor that you wear contact lenses.
\item keep the information to yourself.
\end{enumerate}

\item After completing an experiment, all chemical waste should be
\begin{enumerate}[label=(\alph*)]
\item left at your lab station for the next class.
\item disposed of according to your instructor's directions.
\item dumped in the sink.
\item taken home.
\end{enumerate}

\item You are heating a substance in a test tube. Always point the open end of the tube
\begin{enumerate}[label=(\alph*)]
\item toward yourself.
\item toward your lab partner.
\item toward another classmate.
\item away from all people.
\end{enumerate}

\item Personal eyeglasses provide as much protection as
\begin{enumerate}[label=(\alph*)]
\item  a face shield.
\item  safety glasses.
\item  splash proof chemical goggles.
\item  none of the above.
\end{enumerate}

\item Long hair in the laboratory must be
\begin{enumerate}[label=(\alph*)]
\item cut short.
\item held away from the experiment with one hand.
\item always neatly groomed.
\item tied back or kept entirely out of the way with a hair band, hairpins, or other confining device.
\end{enumerate}

\item In a laboratory, the following should not be worn.
\begin{enumerate}[label=(\alph*)]
\item Loose clothing.
\item Dangling jewelry.
\item Sandals.
\item All of the above.
\end{enumerate}


\item If acid is splashed on your skin, wash at once with
\begin{enumerate}[label=(\alph*)]
\item soap.
\item oil.
\item a weak base.
\item plenty of water.
\end{enumerate}

\item Draw a diagram of your science room and label the locations of the following:\\
%\ding{114} Fire blanket\\
\ding{114} Fire extinguisher(s)\\
\ding{114} Exits\\
\ding{114} Eyewash station\\
\ding{114} Emergency shower\\
\ding{114} Closest fire alarm station\\
\ding{114} Waste disposal container(s)

\item Store your books and bags: 
\begin{enumerate}[label=(\alph*)]
\item  on your lab bench. 
\item  in the aisle between lab benches. 
\item  in a cabinet in the lab. 
\item  under your bench. 
\item  on the top of the instructor's desk. 
\end{enumerate}

\item You are excused from wearing goggles
\begin{enumerate}[label=(\alph*)]
\item if you have permission from your doctor.
\item if they are uncomfortable to wear. 
\item during the lecture in the lab.
\item if you are finished with the experiment.
\item None of the above.
\end{enumerate}

\item If you do not wear goggles during an experiment
\begin{enumerate}[label=(\alph*)]
\item the instructor will suggest you wear them.
\item your instructor will not care.
\item you are not required to wear goggles.
\item you will invited to leave the lab for 15 mins.
\item None of the above.
\end{enumerate}

\item Drinks and food in the lab?
\begin{enumerate}[label=(\alph*)]
\item Are always allowed.
\item Never allowed.
\item Are allowed if you are hungry or thirsty.
\item Are allowed if you are on a diet.
\item None of the above.
\end{enumerate}

\item If you feel ill in the lab
\begin{enumerate}[label=(\alph*)]
\item call your family.
\item ask your coworker to help you do the experiment.
\item tell the instructor.
\item leave immediately.
\item none of the above.
\end{enumerate}
%
%\item You should arrive to the lab
%\begin{enumerate}[label=(\alph*)]
%\item always late.
%\item always on time.
%\item within the first 20 mins.
%\item None of the above.
%\end{enumerate}
%
%\item Thinking about missing a lab session?
%\begin{enumerate}[label=(\alph*)]
%\item You are not allowed to miss any lab sessions.
%\item You are allowed to miss a single lab session.
%\item You can miss two labs if its justified.
%\item None of the above.
%\end{enumerate}
%
%\item When you are done with the experiment
%\begin{enumerate}[label=(\alph*)]
%\item you should stay until the end of the session.
%\item you are allowed to leave.
%\item you should help your coworkers.
%\item none of the above.
%\end{enumerate}
%
%\item The lab counts for the final grade?
%\begin{enumerate}[label=(\alph*)]
%\item Yes. It is 10\% of the grade.
%\item Yes. It is 25\% of the grade.
%\item Nope, it does not count for your grade.
%\item None of the above.
%\end{enumerate}
%
%\item Regarding the lab manual,
%\begin{enumerate}[label=(\alph*)]
%\item you should not bring it to each lab session.
%\item you can bring loose sheets to the lab.
%\item you can bring a photocopy or an e-book.
%\item none of the above.
%\end{enumerate}
%
%\item Regarding the prelab,
%\begin{enumerate}[label=(\alph*)]
%\item you should do it before the lab.
%\item you should do it during the lab.
%\item you can skip it.
%\item None of the above.
%\end{enumerate}
%
%\item Regarding the lab results,
%\begin{enumerate}[label=(\alph*)]
%\item it should be handed the day of the experiment.
%\item It should include two signatures from the instructor.
%\item It can not be handed late.
%\item All of the above.
%\end{enumerate}
%
%\item Can I bring my own googles instead of using the ones provided by you
%\begin{enumerate}[label=(\alph*)]
%\item True
%\item False
%\end{enumerate}
%
%\item Where can you spiral-bind and double-side print  the lab manual
%\begin{enumerate}[label=(\alph*)]
%\item Mcdonalds
%\item Staples
%\item Fedex
%\item Staples and Fedex
%\end{enumerate}
%
%\item This lab manual needs to be spiral-bind and double-side print  because
%\begin{enumerate}[label=(\alph*)]
%\item we need to save paper and trees
%\item You will be tearing out some pages
%\item All of the above
%\end{enumerate}
%
%\item The two-signature rule for a lab report says;
%\begin{enumerate}[label=(\alph*)]
%\item The pre-lab should be signed by your instructor in the lab.
%\item The results of the experiment should be signed by your instructor in in the lab.
%\item When handing the lab  results it has to include two signatures from the instructor.
%\item if you don't have two signatures you won't receive a grade as it means you did not do the work.
%\item All of the above.
%\end{enumerate}
\end{enumerate}
\end{multicols*}

\taburulecolor{black}
 \end{refsection}
 
\end{document}

