\documentclass[cover.tex]{subfiles}


\begin{document} 


\begin{mdframed}[style=MyFrame]
\begin{center}{\textcolor{red}{\Large Lab policies}}\end{center}
\begin{enumerate}
\item You will not be allowed to carry any work in the lab unless you submit all two pages of the lab release form, back and front, via BB.
\item You will not be allowed in the lab unless you bring your safety goggles. Safety glasses will not be permitted.
\item If you are seen once without safety goggles during lab work, the instructor will invite you to leave for 15 minutes. If you are seen twice, you will have to go home.
\item You will not be allowed in the lab unless you bring a printed copy of the corresponding lab experiment to be carried out.
\item In the lab, foods or drinks are not allowed.
\item If you come to the lab with a printed lab experiment which contains missing pages you will be penalized with 5 points. 
\item Pre-lab should be carried out at home and presented to the instructor at the beginning of the experiment. An empty pre-lab page will be collected with your name in case the work is not done.
\item If you are done with the lab work, the instructor will evaluate and signs your work. Lab work without a signature are non gradable.
\item Lab work will be submitted via BB as a single PDF during the lab session, never later than that. Late submissions will be penalized with 5 points a day. 
\item If you finish the lab work late, after the lab ending time, you will be penalized with 5 point.
\item There are no make-ups for missed lab sessions. However, I will allow a single absence without penalty.
\item E-books are not allowed, you need a paper copy of the experiment.
\item If you miss a lab session you miss the grade of the corresponding work carried out during that session.
\item If you arrive late to the lab, after one hour, your lab will not be graded.
\end{enumerate}

    \par\noindent\makebox[1.5in]{\hrulefill}   \hfill\makebox[2.0in]{\hrulefill}    \hfill\makebox[2.0in]{\hrulefill}  \par\noindent\makebox[1.5in][l]{Name}    \hfill\makebox[2.0in][l]{Signature}   \hfill\makebox[2.0in][l]{Date} 

\end{mdframed}

\end{document}