\documentclass[cover.tex]{subfiles}


\begin{document} 


\begin{mdframed}[style=MyFrame]
\begin{center}{\textcolor{red}{\Large Test policies}}\end{center}
\begin{enumerate}


\item	You are a valuable and capable student, able to solve the questions on this quiz, and much more
\item	In your education, you get what you put on. Strive for perfection in everything you do. No one can remove what you have learned. They can steal your money though.
\item	Life is hard, and this quiz might be hard as well. You might not be able to finish this quiz; do as much as you can
\item	Do not be discouraged. The goal here is not to punish you but for you to realize the concepts you may not have mastered yet so you can review 
\item	We all make mistakes, me as well; just try to be wrong less than you are right 
\item	You are not allowed to use here most devices (phones, computers, watches, TV), but you can use a much more useful device, your calculator (graphing for 202, scientific for 201, basic calculator 121), and your mind
\item	You are not allowed to copy. If you do and I notice, know that I will not intervene or even let you know I noticed. At the end of the semester, when grades are submitted, your grade will be updated to an F (sorry but you know better)
\item	Once you start this test you are not allowed to leave the room. Use the restroom before entering the testing room
\item	You are allowed to bring a formula sheet made of no more than one 8.5x11 in page
\item Once you finish the test you need to leave the testing room. Go and have a coffee or tea
\item	Finally, I am grateful for the time we spend together in class, given that time is limited


\end{enumerate}

    \par\noindent\makebox[1.5in]{\hrulefill}   \hfill\makebox[2.0in]{\hrulefill}    \hfill\makebox[2.0in]{\hrulefill}  \par\noindent\makebox[1.5in][l]{Name}    \hfill\makebox[2.0in][l]{Signature}   \hfill\makebox[2.0in][l]{Date} 

\end{mdframed}

\end{document}
